%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}

\special{papersize=8.5in,11in}

\usepackage{cite}
\usepackage{color}
\usepackage{epsfig}
\usepackage{pslatex}
\usepackage{bm}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{eucal}
\usepackage{mathrsfs}
\usepackage{listings}
\usepackage{hyperref}


\input{def}

\textwidth 16.0cm
\textheight 23.0cm
\topmargin 0cm
\headheight 0cm
\headsep 0cm
\topskip 0cm
\oddsidemargin 0.00cm
\evensidemargin 0.00cm
%\addtolength{\textheight}{1in}

%\renewcommand{\baselinestretch}{1.5}\small\normalsize % double spacing
%\renewcommand{\baselinestretch}{0.7}\small\normalsize % single spacing
%\small % smaller font
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\centerline{\Large\bf UQTk Manual: Surrogate construction and global sensitivity analysis} 
\medskip
\centerline{UQTk group}
\centerline{Sandia National Laboratories, Livermore, CA}
\centerline{\today}
\medskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Overview}
\label{sec:uqoverview}
UQTk (\url{www.sandia.gov/UQToolkit}) is a lightweight C++ library, developed in Sandia National Laboratories, California, 
that primarily offers tools for surrogate model construction and uncertainty propagation with 
polynomial chaos expansions (PCE), as well as model calibration and validation.

UQTk Version 2.0 is released under the GNU Lesser General Public License (LGPL). 

\section{Download and compilation}
\label{sec:uqdownload}

A tar-ball with the source code, tutorials, examples and documentation can be 
downloaded from \url{www.sandia.gov/UQToolkit/uqtk\_download.html}

Before compilation, one should set a file \texttt{config/config.site} with computer-specific compilation options. 
Both C++ and Fortran compilers are required. The file \texttt{config/config.gnu} provides a good 
starting point as a sample configuration file.

Compilation is simply invoked by 
\begin{ShellCmd}
make all
\end{ShellCmd}


\section{Structure}
\label{sec:uqstruct}

Below we present parts of the UQTk structure that are relevant to the current study.

\begin{itemize}
\item \texttt{config}: configuration file location
\item \texttt{doc\_cpp}: doxygen documentation
\item \texttt{src\_cpp}: source code - all libraries reside here
\subitem \texttt{src\_cpp/lib}: location of all compiled libraries in C++ and Fortran
\subitem \texttt{src\_cpp/apps}: command line utilities for performing various UQ tasks (source codes)
\subitem \texttt{src\_cpp/bin}: command line utilities for performing various UQ tasks (executables)
\item \texttt{examples\_cpp}: example codes and scripts
\subitem \texttt{examples\_cpp/uq\_surr}: current set of scripts that automates the forward UQ task utilizing the command line \texttt{apps} above.
\end{itemize}

\section{Forward UQ: surrogate construction and global sensitivity analysis}
\subsection*{Theory}
See the central Manual.

\input{bash_old}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
